---
title: "load2scalpelDB"
author: "Anatoly Sorokin"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
  html_document: default
params:
  format: !r if(opts_knit$get("rmarkdown.pandoc.to") == 'html') c('screen', 'print')
    else 'print'
  version: !r if(nchar(Sys.which("git"))) system("git describe --long --dirty --abbrev=10  --tags  --always",
    intern=TRUE) else date()
header-includes:
- \usepackage[T2A]{fontenc}
- \usepackage[utf8]{inputenc}
- \usepackage[english,russian]{babel}
- \usepackage{grffile}
- \usepackage{rotating}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage{lscape}
---
```{r loadPackages, include=FALSE, cache=FALSE}
## load additional packages in this chunk
library(pander)
library(knitr)
#library('Matrix')
library(ggplot2)
library(data.table)
library(plyr)
library(xtable)
#library(xcms)
#library("FactoMineR")
#library(cluster)
#library(dendextend)
#library(factoextra)
#library(corrplot)
library(ncdf4)
#library("PerformanceAnalytics")
#library("pvclust")
#library("sda")
library(RColorBrewer)
library(MALDIquant)
library(MALDIquantForeign)
library(DBI)
library(MonetDB.R)
ticThreshold<-0.01
absTicThreshold<-1000
```

```{r setup, include=FALSE, cache=FALSE}
## This chunk should contain global configuration commands.
## Use this to set knitr options and related things. Everything
## in this chunk will be included in an appendix to document the
## configuration used.
#output <- opts_knit$get("rmarkdown.pandoc.to")
opts_knit$set(stop_on_error = 2L)

## By default R code is only included in HTML versions of the report
## (where it can be collapsed). You can generate a PDF version
## using rmarkdown::pdf_document to get a copy for print. Extensive
## chunks of R code may or may not be desired in /hat setting. If you
## want them simply change the following arguments to `echo = TRUE`.
## In either case the default can be overwritten for individual chunks.
#opts_chunk$set(echo = output=="html")
#opts_chunk$set(warning = output=="html")
#opts_chunk$set(message = output=="html")

## Cache options
opts_chunk$set(cache=FALSE)

## Figure options
## Set default figure format
#options(reportmd.figure.format=params$format)

## Set 'hide.fig.code' to FALSE to include code chunks that
## produce Figures in the output. Note that this affects all chunks
## that provide a figure caption.
opts_chunk$set(hold=TRUE, hide.fig.code=FALSE)

## Set up default plotting options for different formats.
## These can be overwritten for individual chunks
#interactiveFig()
#screenFig()
#printFig()

## Pander options
panderOptions("digits", 3)
panderOptions("table.split.table", 160)

## Configure Figure and Table lables
#options(figcap.prefix = "Figure", figcap.sep = ":", figcap.prefix.highlight = "**")
#options(tabcap.prefix = "Table", tabcap.sep = ":", tabcap.prefix.highlight = "**")

## Install required knitr hooks
#installHooks()
```

```{r functions, include=FALSE}
## Custom functions used in the analysis should go into this chunk.
## They will be listed in their own section of the appendix.
printTable <-
  function(mat,main,landscape = TRUE,digits = 0,sig = 0.01,align= 'lllrr') {
    addtorow          <- list()
    addtorow$pos      <- list()
    addtorow$pos[[1]] <- c(0)
    addtorow$command  <- c(
      paste(
        "\\hline \n",
        "\\endhead \n",
        "\\hline \n",
        "\\multicolumn{3}{l}{\\footnotesize Continued on next page} \n",
        "\\endfoot \n",
        "\\endlastfoot \n",sep = ""
      )
    )
    subset <- 'anode'
    if (landscape) {
      cat(
        sprintf(
          "\\newpage\n  \\begin{landscape} \n\\begin{center}\n\\captionof{table}{Table, %s (%d OTUs)}\n\\scriptsize",
          main,dim(mat)[1]
        )
      )
    }else{
      cat(
        sprintf(
          "\\begin{center}\n\\captionof{table}{Table, %s (%d OTUs)}\n\\scriptsize",
          main,dim(mat)[1]
        )
      )
    }
    #cat(dim(mat),names(mat),'\n')
    matU<-mat
    # matU$name<-sanitizestr(mat$name)
    # matU$description<-sanitizestr(mat$description)
    # cat(dim(matU),names(matU),'\n')
    print(
      xtable(
        matU,
        align = align,#paste(align,collapse = ''),
        digits = digits)
      ,size = "small",include.colnames = TRUE,
      tabular.environment = "longtable", sanitize.text.function=NULL,#function(.x)sanitizestr(stri_escape_unicode(.x)),
      floating = FALSE,include.rownames = FALSE,add.to.row = addtorow,hline.after =
        c(-1)
    )
    if (landscape) {
      cat("\\end{center}\n \\end{landscape}")
    }else{
      cat("\\end{center}\n ")
    }
    
  }
##==================== Functions ====================##

writeDTpeak<-function(id,scanDF,tic,peak,fname){
  p<-peak[[id]]
  md<-metaData(p)
  if(length(p)>0){
    scanID<-scanDF$id[scanDF$num==md$number]
  #cat('Writing scan',md$number,md$retentionTime,'\n')
  resDF<-data.table(scan=scanID,
                    mz=p@mass,
                    intensity=tic[id]*p@intensity,
                    norm2tic=p@intensity,
                    sqrtnorm2tic=sqrt(p@intensity),
                    sqrtintensity=sqrt(tic[id]*p@intensity),
                    snr=p@snr)
  if(file.exists(fname)){
  	app=TRUE
  }else{
  	app=FALSE
  }
  fwrite(resDF,file=fname,col.names=FALSE,append=app,quote=FALSE,sep='|',row.names=FALSE,na='')
  }
}

panderCnt<-function(d){
  w<-dim(d)[2]
  inCol<-sapply(d,is.numeric)
  j<-rep('left',w)
  j[inCol]<-'right'
  pander(d, justify = j)
}

```

```{r queries, include=FALSE}
##==================== SQL queries ====================##
insertComment<-paste('insert into comment(dt,comment,author) values (now(),?,?)')
getCommentID<-'SELECT ID FROM comment where comment=?'
insertCommentRef<-paste('insert into spectrum_comment(spectrumid,commentid) values (?,?)')
insertSpectrum<-paste("INSERT INTO spectrum ",
                      "  (SampleTumorPatientID, ",
                      "  SampleTumorID, ",
                      "  SampleID, ",
                      "  ResolutionID, ",
                      "  Solvent, ",
                      "  Device, ",
                      "  dt, ",
                      "  FileName, ",
                      "  ionsource, ",
                      "  mode,mzrange,exptype) ",
                      "VALUES (?,?,?,?,?,?,?,?,?,?,?,?);")
insertPatient<-'insert into patient (emsid,yob) values(?,-1)'
insertTissue<-'insert into tissue (patientid,label,diagnosis) values (?,?,1)'
insertSample<-'insert into smpl (tumorpatientid,tumorid,label) values (?,?,?)'
getSpecID<-"SELECT ID FROM spectrum where filename like ?";
getPatient<-'select id,emsid,yob,sex from patient where emsid like ?'
getTissue<-'select t.id,t.patientid,t.label,t.dt from tissue t join patient p on p.id=t.patientid where p.id=? and t.label like ?' 
getSample<-'select s.id,s.label as name, \'tissue: "\'||t.label||\'"; patient: "\'|| p.emsid||\'"\' as description from smpl s,tissue t, patient p where t.id=s.tumorid and s.tumorpatientid=p.id and p.id=? and t.id=? and s.label like ? ;'
insertScan<-paste("INSERT INTO scan",
                  "  (SpectrumID, ",
                  "  num, ",
                  "  rt, ",
                  "  tic) ",
                  "VALUES (?, ?, ?, ?);")
getScanID<-'SELECT ID FROM scan where spectrumid=? and num=?'
getSpectrum<-paste('select id,emsid,dt,diagnosis,',
                   'filename,device,min,max,exptype,',
                   'mode,resolution ',
                   'from files ',
                   'where filename like ?')
getScans<-'select c.* from spectrum s join scan c  on s.id=c.spectrumid where filename like ?'

emptyPeaksQ<-paste('select s.id,filename, ',
                   'count(distinct c.id) scn  ',
                   'from spectrum s join scan c ',
                   'on s.id=c.spectrumid ',
                   'where c.id in ',
                   '(select id as scan from scan ',
                   'except select scan from peak) ',
                   'and filename like ?',
                   'group by s.id,filename',
                   'order by s.id asc')
emptyScansQ<-paste('select s.id,filename,count(distinct c.id) scans',
                   'from spectrum s left join scan c on s.id=c.spectrumid ',
                   'where filename like ?',
                   'group by s.id,filename having count(distinct c.id)=0;')

```

```
{r oblig.par}
dbname = "msinvent"
usr='msinvent'
pwd='msinvent'
dtPath = '/Volumes/AS_WD_HFS/Scalpel/DBData/'
cdf.file='/Users/lptolik/Yandex.Disk.localized/BD_cdf/1_02_495_MetCl_2_FT100k.cdf'
devID<-1 #Device
solID<-6 #Solvent
isID<-1 # ionsource
resID<-1 #ResolutionID
smplID<-1 #SampleID
stID<-1 #SampleTumorID
stpID<-1 #SampleTumorPatientID
nMode<-1 #Negative mode
```

# Read data
Before running the code a number of variables should be setted for appropriate data loading:
 
 1. the path to the folder where data will be moved after upload *dtPath* 
 3. the name of the database *dbname*
 4. user/password for teh database: *usr* and *pwd*
 

Для работы необходим параметр `cdf.file`, который содержит полный путь к обрабатываемому файлу. В базу будут загружено содержимое файла `cdf.file`

```{r check.values}
load(file = 'spectra.RData')
if(!(exists('dbname')&
     exists('usr')&
     exists('pwd')&
     exists('dtPath')&
     exists('solID')&
     exists('isID')&
     exists('cdf.fname')& #CDF file not needed any more it was processed by prepare4db, but its name should be loaded into database
     exists('smplID')&
     exists('stID')&
     exists('stpID'))){
  stop('not all obligatory parameters are provided\n')
}
if(!exists('halfWindowSize')){
  halfWindowSize<-3 # best suited for centroided data
}
```

# Load prepared data 
```{r load.data.from.rdat}
tic<-sapply(origSpectra,totalIonCurrent)
imTIC<-which.max(tic)
qth<-max(absTicThreshold,quantile(tic,probs = ticThreshold))
experimentData<-ncMD$experiment_date_time_stamp
if(is.na(exData)){
if(is.null(ncMD$created_by)){
  exData<-as.POSIXlt.character(experimentData,format='%Y%m%d%H%M%S%z')
}else {
  exData<-as.POSIXlt.character(experimentData,format='%m/%d/%Y %H:%M:%OS')
}}
fileData<-ncMD$netcdf_file_date_time_stamp
origFilePath<-ncMD$source_file_reference
comment<-ncMD$administrative_comments
```

```{r plot.max}
which.max(spectra[[imTIC]]@intensity)->imTICmax
plot(spectra[[imTIC]], type="b",xlim=c(-1,1)+spectra[[imTIC]]@mass[imTICmax])
```

# Connect to the database

```{r db.connect}
proceedFile<-TRUE
conn <- dbConnect(MonetDB.R::MonetDB(), 
                  dbname = dbname,
                  user=usr,password=pwd,timeout=2400)
spectrumID<-dbGetQuery(conn,getSpecID,paste0(cdf.fname,'_%'))
if(dim(spectrumID)[1]>0){
  scID<-dbGetQuery(conn,emptyScansQ,paste0(cdf.fname,'_%'))
  if(dim(scID)[1]==0){
    pID<-dbGetQuery(conn,emptyPeaksQ,paste0(cdf.fname,'_%'))
    if((dim(pID)[1]==0)){
      proceedFile<-FALSE
    }
  }
}
  
#proceedFile<-(dim(spectrumID)[1]==0)

```

```{r emptyScans}
panderCnt(scID)
```

```{r emptyPeaks}
panderCnt(pID)
```

# Загрузка данных с помощью MALDIquant

Текущее значение параметра `cdf.file`:

`r cdf.file`
`r proceedFile`

```{r load.cdf,cache=TRUE, eval=proceedFile}
plot(tic)
abline(h = qth)
#spectra <- trim(spectra,range = mzrange)
```

# Load data to DB
```{r db.fetch, eval=proceedFile}
devices<-dbReadTable(conn,'device')
idxDev<-which(devices$id==devID)
solvents<-dbReadTable(conn,'solvent')
idxSol<-which(solvents$id==solID)
ionSources<-dbReadTable(conn,'ionsource')
idxIS<-which(ionSources$id==isID)
resolutions<-dbReadTable(conn,'resolution')
modes<-dbReadTable(conn,'mode')
ranges<-dbReadTable(conn,'mzrange')
note<-paste('exDT:',experimentData,'\nfileDT:',
            fileData,'\norigFile:',
            origFilePath,'\ncomment:',comment)
```

```{r prepare.sample, eval=proceedFile}
patient<-dbGetQuery(conn,getPatient,stpID)
if(dim(patient)[1]==0){
  rs<-dbSendStatement(conn,insertPatient,stpID)
  patient<-dbGetQuery(conn,getPatient,stpID)
}
tissue<-dbGetQuery(conn,getTissue,patient$id,stID)
if(dim(tissue)[1]==0){
  rs<-dbSendStatement(conn,insertTissue,patient$id,stID)
  tissue<-dbGetQuery(conn,getTissue,patient$id,stID)
}
sample<-dbGetQuery(conn,getSample,patient$id,tissue$id,as.character(smplID))
if(dim(sample)[1]==0){
  rs<-dbSendStatement(conn,insertSample,patient$id,tissue$id,as.character(smplID))
  sample<-dbGetQuery(conn,getSample,patient$id,tissue$id,as.character(smplID))
}
```


The data loaded with the following properties:
```{r prop.table, eval=proceedFile}
parName<-c('Sample','Device','Ion source','Solvent')
resDF<-cbind(data.frame(Parameter=parName),
             rbind(sample,
                   devices[idxDev,c(1,2,4)],
                   ionSources[idxIS,],
                   data.frame(id=solvents$id[idxSol],
                              name=solvents$name[idxSol],
                              description=solvents$composition[idxSol])
                   )
               
             )
kable(resDF, format = "latex", caption = 'Predefined parameters for load', row.names=FALSE, booktabs=TRUE)
```

According to the protocol other parameters are as follows:
```{r protocol.table, eval=proceedFile}
pr<-sapply(mdL,function(.x).x$protocol)
mdLdf<-unique(ldply(mdL,function(.x)as.data.frame(.x)))
kable(mdLdf, format = "latex", caption = 'Predefined parameters for protocol', row.names=FALSE, booktabs=TRUE)
```

```{r already.loaded,eval=!proceedFile}
cat('The file with name \n"',cdf.file,'"\n already loaded into the database\n')
```
 

## Spectrum
```{r insert.spectrums, eval=proceedFile}
for(sidx in unique(intRT)){
  cdf.fid<-paste0(cdf.fname,'_',sidx)
  spectrumID<-dbGetQuery(conn,getSpecID,cdf.fid)
    rtIdx<-which(intRT==sidx)[1]
    idxRes<-which(resolutions$name==mdL[[rtIdx]]$Detector)
    resID<-resolutions$id[idxRes]
    nMode<-ifelse(mdL[[rtIdx]]$Polarity=='Neg',1,2)
    rangeID<-ifelse(mdL[[rtIdx]]$Range=="100-2000",1,2)
  if(dim(spectrumID)[1]==0){
    # idxMode<-which(modes$id==nMode)
    # idxRange<-which(ranges$id==rangeID)
    rs<-dbSendStatement(conn,insertSpectrum,
                        patient$id, #patient
                        tissue$id, #tumor
                        sample$id,# samlpe
                        resID,# resolution
                        solID,# solution
                        devID,# device
                        exData, # experimental data
                        cdf.fid,
                        isID,# ionsource
                        nMode,# mode
                        rangeID, #range
                        expType
    )
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
    spectrumID<-dbGetQuery(conn,getSpecID,cdf.fid)
    rs<-dbSendStatement(conn,insertComment,note,'autoloader')
    commentID<-dbGetQuery(conn,getCommentID,note)
    rs<-dbSendStatement(conn,insertCommentRef,spectrumID$id,commentID$id)
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
  }
}
```

```{r show.spectra,results='asis'}
specT<-dbGetQuery(conn,getSpectrum,paste0(cdf.fname,'%'))
printTable(specT,main="Loaded spectra",landscape = TRUE,digits=0,align = 'lllllllrrlll')
```

## Scans

```{r insert.scans, eval=proceedFile}
scanDF<-dbGetQuery(conn,getScans,paste0(cdf.fname,'_%'))
if(dim(scanDF)[1]==0){
df<-data.frame(spectrumID=1,scanid=1,mz=0.01,intensity=0.01)[FALSE,]
for(sidx in unique(intRT)){
  cdf.fid<-paste0(cdf.fname,'_',sidx)
  spectrumID<-dbGetQuery(conn,getSpecID,cdf.fid)
  for(sp in origSpectra[intRT==sidx]){
    md<-metaData(sp)
    rs<-dbSendStatement(conn,insertScan,
                        spectrumID$id,
                        md$number,
                        md$retentionTime,totalIonCurrent(sp))
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
  }
}
scanDF<-dbGetQuery(conn,getScans,paste0(cdf.fname,'_%'))
}
#spectrumID<-dbGetQuery(conn,getSpecID,basename(cdf.file))
```

```{r show.scans,results='asis',eval=proceedFile}
printTable(scanDF,main="Loaded scans",landscape = FALSE,digits=2,align = 'lrrrrr')
```


## Peaks

Таблица *Peaks* содержит выделенные из сырых данных пики, для улучшения качества данных все сканы выравниваются по отношению к скану с максимальным TIC, пики группируются с отностительной точностью 2e-5 и исключаются пики, встречающиеся менее чем в 25% сканов. 

### Disable referential constraints and indices
```
{r drop.peak.constraints}
rs<-dbSendStatement(conn,'alter table peak drop CONSTRAINT "peak_featureFK";')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
rs<-dbSendStatement(conn,'alter table peak drop CONSTRAINT "peak_scanFK";')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
rs<-dbSendStatement(conn,'drop INDEX "peak_mz";')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
rs<-dbSendStatement(conn,'drop INDEX "peak_scan";')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
```

```{r prepare.peak.file, eval=proceedFile}
peakFname<-normalizePath(paste0(dirname(knitr::current_input(dir = TRUE)),'/tmp_peak.tsv'))
#system(paste0('gunzip ',peakFname,'.gz'))
peakFname
```


```{r preprocess.peak.file, eval=proceedFile}
system.time(res<-sapply(c(1:dim(featureMatrix2)[1]),writeDTpeak,scanDF,tic=tic2,peak=peaks2,fname=peakFname))

```

```{r load.peak.file, eval=proceedFile}
system(paste0('mclient  -d msinvent  -s  "COPY INTO ',
              ' ms.peak(scan,mz,intensity,norm2tic,sqrtnorm2tic,sqrtintensity,snr)',
              '  FROM ',"'",peakFname,
              "'(scan,mz,intensity,norm2tic,sqrtnorm2tic,sqrtintensity,snr)",';"'),
       intern = TRUE)->mcOut
mcOut
system2('wc', peakFname,stdout=TRUE)->wc
wc
wcn<-as.numeric(unlist(strsplit(trimws(wc),' ')))
wcn
#system(paste0('gzip ',peakFname))
```

```{r populate.peak.table, eval=proceedFile}
before<-dbGetQuery(conn,'select count(*) as num from peak;')
before
for(sidx in unique(intRT)){
  cdf.fid<-paste0(cdf.fname,'_',sidx)
spectrumID<-dbGetQuery(conn,getSpecID,cdf.fid)
rs<-dbSendStatement(conn,
                        paste('INSERT INTO peak(mz,scan,intensity,norm2tic,sqrtnorm2tic,sqrtintensity,snr) ',
'(select mz,s.id as scan, intensity, norm2tic, ',
'        SQRT(norm2tic) as sqrtnorm2tic,  ',
'        SQRT(intensity) as sqrtintensity, snr ',
'from (select p.id from (select * from tmp_peak limit 1) t, ',
'      spectrum p  where p.filename like t.spec) sp, ',
'      tmp_peak t, scan s where s.spectrumid=sp.id and s.num=t.num );'))
after<-dbGetQuery(conn,'select count(*) as num from peak;')
after
if((after$num>before$num) & (after$num-before$num==wcn[1]) ){
  rs<-dbSendStatement(conn,'delete from tmp_peak;')
}
abDF<-data.frame(tsv=wcn[1],before=before$num,after=after$num,diff=(after$num-before$num))
kable(abDF, format = "latex", caption = 'Predefined parameters for load', row.names=FALSE, booktabs=TRUE)
}
```


### Enable referential constraints
```
{r add.peak.constraints}
rs<-dbSendStatement(conn,'ALTER TABLE "ms"."peak" ADD CONSTRAINT "peak_featureFK" FOREIGN KEY ("feature") REFERENCES "ms"."features" ("id");')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
rs<-dbSendStatement(conn,'ALTER TABLE "ms"."peak" ADD CONSTRAINT "peak_scanFK" FOREIGN KEY ("scan") REFERENCES "ms"."scan" ("id");')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
rs<-dbSendStatement(conn,'CREATE INDEX "peak_mz" ON "ms"."peak" ("mz");')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)
rs<-dbSendStatement(conn,'CREATE INDEX "peak_scan" ON "ms"."peak" ("scan");')
    dbHasCompleted(rs)
    dbGetRowsAffected(rs)
    dbClearResult(rs)

```

## Features

# Save data
```{r prepare.fname}
res.afname<-paste0(dtPath,spectrumID$id,'.peaks.RData')
cdf.afname<-paste0(dtPath,spectrumID$id,'.cdf')
```

Loaded spectra saved in `r res.afname` and original CDF file saved in `r cdf.afname`

```{r save.data}
save(spectra,origSpectra,ncMD,peaks,peaks0,peaks2,fpeaks2,featureMatrix2,devID,solID,isID,resID,smplID,stID,stpID,rangeID,nMode,mdL,cdf.file,cdf.fname,spectrumID,patient,tissue,sample,file = res.afname)
file.copy(cdf.file,cdf.afname)
```

# Appendix {.tabset}
## Functions
```{r functions, eval=FALSE, include=TRUE}
```

```{r queries, eval=FALSE, include=TRUE}
```

## Setup R
```{r setup, eval=FALSE}
```

## Versions
### Document version
```{r docVersion, echo=FALSE, results='asis', cache=FALSE}
cat(params$version)
```

### Session Info
```{r sessionInfo, echo=FALSE, results='asis', class='text', warning=FALSE}
pander(devtools::session_info())
```

