---
title: "load2scalpelDB"
author: "Anatoly Sorokin"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
  html_document: default
params:
  format: !r if(opts_knit$get("rmarkdown.pandoc.to") == 'html') c('screen', 'print')
    else 'print'
  version: !r if(nchar(Sys.which("git"))) system("git describe --long --dirty --abbrev=10  --tags  --always",
    intern=TRUE) else date()
header-includes:
- \usepackage[T2A]{fontenc}
- \usepackage[utf8]{inputenc}
- \usepackage[english,russian]{babel}
- \usepackage{grffile}
- \usepackage{rotating}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage{lscape}
---
```{r loadPackages, include=FALSE, cache=FALSE}
## load additional packages in this chunk
library(pander)
library(knitr)
#library('Matrix')
library(ggplot2)
library(data.table)
#library(plyr)
library(xtable)
#library(xcms)
#library("FactoMineR")
#library(cluster)
#library(dendextend)
#library(factoextra)
#library(corrplot)
library(ncdf4)
#library("PerformanceAnalytics")
#library("pvclust")
#library("sda")
library(RColorBrewer)
library(MALDIquant)
library(MALDIquantForeign)
ticThreshold<-0.01
absTicThreshold<-1000
```

```{r setup, include=FALSE, cache=FALSE}
## This chunk should contain global configuration commands.
## Use this to set knitr options and related things. Everything
## in this chunk will be included in an appendix to document the
## configuration used.
#output <- opts_knit$get("rmarkdown.pandoc.to")
opts_knit$set(stop_on_error = 2L)

## By default R code is only included in HTML versions of the report
## (where it can be collapsed). You can generate a PDF version
## using rmarkdown::pdf_document to get a copy for print. Extensive
## chunks of R code may or may not be desired in /hat setting. If you
## want them simply change the following arguments to `echo = TRUE`.
## In either case the default can be overwritten for individual chunks.
#opts_chunk$set(echo = output=="html")
#opts_chunk$set(warning = output=="html")
#opts_chunk$set(message = output=="html")

## Cache options
opts_chunk$set(cache=FALSE)

## Figure options
## Set default figure format
#options(reportmd.figure.format=params$format)

## Set 'hide.fig.code' to FALSE to include code chunks that
## produce Figures in the output. Note that this affects all chunks
## that provide a figure caption.
opts_chunk$set(hold=TRUE, hide.fig.code=FALSE)

## Set up default plotting options for different formats.
## These can be overwritten for individual chunks
#interactiveFig()
#screenFig()
#printFig()

## Pander options
panderOptions("digits", 3)
panderOptions("table.split.table", 160)

## Configure Figure and Table lables
#options(figcap.prefix = "Figure", figcap.sep = ":", figcap.prefix.highlight = "**")
#options(tabcap.prefix = "Table", tabcap.sep = ":", tabcap.prefix.highlight = "**")

## Install required knitr hooks
#installHooks()
```

```{r functions, include=FALSE}
## Custom functions used in the analysis should go into this chunk.
## They will be listed in their own section of the appendix.

##==================== Functions ====================##
writeDTsignal<-function(sp,specID,fname){
  md<-metaData(sp)
  #cat('Writing scan',md$number,md$retentionTime,'\n')
  resDF<-data.table(spec=specID,
                    num=md$number,
                    mz=sp@mass,
                    intensity=sp@intensity)
  if(file.exists(fname)){
  	app=TRUE
  }else{
  	app=FALSE
  }
  fwrite(resDF,file=fname,col.names=FALSE,append=app,quote=FALSE,sep='|',row.names=FALSE,na='')
}

writeDTpeak<-function(id,specID,tic,peak,fname){
  p<-peak[[id]]
  md<-metaData(p)
  if(length(p)>0){
  #cat('Writing scan',md$number,md$retentionTime,'\n')
  resDF<-data.table(spec=specID,
                    num=md$number,
                    mz=p@mass,
                    intensity=tic[id]*p@intensity,
                    norm2tic=p@intensity,snr=p@snr)
  if(file.exists(fname)){
  	app=TRUE
  }else{
  	app=FALSE
  }
  fwrite(resDF,file=fname,col.names=FALSE,append=app,quote=FALSE,sep='|',row.names=FALSE,na='')
  }
}

```

```
{r oblig.par}
dtPath = '/Volumes/AS_WD_HFS/Scalpel/DBData/'
cdf.file<-"/Volumes/AS_WD_HFS/Scalpel/BD_cdf/0_00_1178-15_FT100k.cdf"
#  '/Users/lptolik/Yandex.Disk.localized/BD_cdf/1_02_495_MetCl_2_FT100k.cdf'
devID<-1 #Device
solID<-6 #Solvent
isID<-1 # ionsource
resID<-1 #ResolutionID
smplID<-1 #SampleID
stID<-1 #SampleTumorID
stpID<-1 #SampleTumorPatientID
nMode<-1 #Negative mode
rangeID<-1 #MZrange
specID<-'name of the spec' # 
cdf.fname
```

# Read data
Before running the code a number of variables should be setted for appropriate data loading:
 
 1. the path to the folder where data will be moved after upload *dtPath* 
 2. the references to device *devID*, solvent *solID*, ion source *isID*, resolution *resID*, mode *nMode*, mz range *rangeID*
 3. the name of the database *dbname*
 4. user/password for teh database: *usr* and *pwd*
 

Для работы необходим параметр `cdf.file`, который содержит полный путь к обрабатываемому файлу. В базу будут загружено содержимое файла `cdf.file`

```{r check.values}
if(!(exists('devID')&
     exists('solID')&
     exists('isID')&
     exists('resID')&
     exists('smplID')&
     exists('stID')&
     exists('stpID')&
     exists('rangeID')&
     exists('nMode')&
      exists('cdf.fname')&
     exists('cdf.file'))){
  stop('not all obligatory parameters are provided\n')
}
if(!exists('halfWindowSize')){
  if(resID==1){
  halfWindowSize<-3 # best suited for centroided data
}else{
  halfWindowSize<-5
}
}
if(!exists('tolerance')){
  tolerance = 2e-4 
}
ncMD<- ncatt_get(nc_open(cdf.file),0)
experimentData<-ncMD$experiment_date_time_stamp
fileData<-ncMD$netcdf_file_date_time_stamp
origFilePath<-ncMD$source_file_reference
comment<-ncMD$administrative_comments
```

# Загрузка данных с помощью MALDIquant

Текущее значение параметра `cdf.file`:

`r cdf.file`

```{r load.cdf,cache=TRUE}
spectra<-import(cdf.file,verbose=TRUE)
if(any(sapply(spectra, MALDIquant::isEmpty))){
  spectra<-spectra[!sapply(spectra, MALDIquant::isEmpty)]
}
mzWidth<-sapply(spectra, function(.x)diff(range(.x@mass)))
if(any(mzWidth<0.2*max(mzWidth))){
  spectra<-spectra[mzWidth>=0.2*max(mzWidth)]
}
#hist(sapply(spectra, length))
tic<-sapply(spectra,totalIonCurrent)
eic300<-sapply(trim(spectra,range = c(0,350)),totalIonCurrent)
eic1000<-sapply(trim(spectra,range = c(400,1000)),totalIonCurrent)
time<-sapply(spectra,function(.x)metaData(.x)$retentionTime)
qtic<-quantile(tic,probs = seq(0, 1, 0.1),names = TRUE)
qth<-max(absTicThreshold,quantile(tic,probs = ticThreshold))
#plot(xraw@tic,tic)
plot(tic)
abline(h = qth)
spectra <-spectra[tic>qth]
tic<-sapply(spectra,totalIonCurrent)
#spectra <- trim(spectra,range = mzrange)
imTIC<-which.max(tic)
plot(spectra[[imTIC]])
```

```{r save.sig}
save(spectra,ncMD,devID,solID,isID,resID,smplID,stID,stpID,rangeID,nMode,cdf.file,cdf.fname,file = 'spectra.RData')

```


## Signal

```{r plot.palmitate}
palmMZ<-255.24
palmID<-which((spectra[[imTIC]]@mass<=(palmMZ+1))&(spectra[[imTIC]]@mass>=(palmMZ-1)))
if(length(palmID)>10){
plot(spectra[[imTIC]], type="b",xlim=c(-1,1)+palmMZ)
}
```
```{r plot.stearate}
stearMZ<-283.27
stearID<-which((spectra[[imTIC]]@mass<=(stearMZ+1))&(spectra[[imTIC]]@mass>=(stearMZ-1)))
if(length(stearID)>10){
plot(spectra[[imTIC]], type="b",xlim=c(-1,1)+stearMZ,ylim=range(spectra[[imTIC]]@intensity[stearID]))
}
```
```{r plot.max}
which.max(spectra[[imTIC]]@intensity)->imTICmax
plot(spectra[[imTIC]], type="b",xlim=c(-1,1)+spectra[[imTIC]]@mass[imTICmax])
```



```
{r prepare.signal.file, eval=proceedFile}
sigFname<-normalizePath(paste0(dirname(knitr::current_input(dir = TRUE)),'/tmp_signal.tsv'))
system.time(res<-sapply(spectra,writeDTsignal,specID=basename(cdf.file),fname=sigFname))
```

## Peaks

Таблица *Peaks* содержит выделенные из сырых данных пики, для улучшения качества данных все сканы выравниваются по отношению к скану с максимальным TIC, пики группируются с отностительной точностью 2e-5 и исключаются пики, встречающиеся менее чем в 25% сканов. 
```{r align.spectra}
origSpectra<-spectra
spectra <- calibrateIntensity(spectra, method="TIC")
calibrSpectra<-spectra
peaks0<-detectPeaks(spectra, SNR=1, halfWindowSize=halfWindowSize,
                       method="SuperSmoother")
spectra <- alignSpectra(spectra,reference = spectra[[imTIC]], halfWindowSize = halfWindowSize,tolerance = tolerance)
alSpectra<-spectra

```

```{r prepare.peaks, cache=TRUE}
peaks <- detectPeaks(spectra, SNR=1, halfWindowSize=halfWindowSize,
                       method="SuperSmoother")
idx<-which(sapply(peaks,length)>10)
peaks2 <- binPeaks(peaks[idx],method = 'strict',tolerance = tolerance)
fpeaks2 <- filterPeaks(peaks2, minNumber = 10)
featureMatrix2 <- intensityMatrix(fpeaks2, spectra)

```

```{r prepare.peak.file}
peakFname<-normalizePath(paste0(dirname(knitr::current_input(dir = TRUE)),'/tmp_peak.tsv'))
system.time(res<-sapply(c(1:length(fpeaks2)),writeDTpeak,specID=cdf.fname,tic=tic,peak=fpeaks2,fname=peakFname))
```

# Save data
```{r save.data}
save(spectra,origSpectra,ncMD,peaks,peaks0,peaks2,fpeaks2,featureMatrix2,devID,solID,isID,resID,smplID,stID,stpID,rangeID,nMode,cdf.file,cdf.fname,file = 'spectra.RData')
```

# Appendix {.tabset}
## Functions
```{r functions, eval=FALSE, include=TRUE}
```

## Setup R
```{r setup, eval=FALSE}
```

## Versions
### Document version
```{r docVersion, echo=FALSE, results='asis', cache=FALSE}
cat(params$version)
```

### Session Info
```{r sessionInfo, echo=FALSE, results='asis', class='text', warning=FALSE}
pander(devtools::session_info())
```

