---
title: "scalpelDB report"
author: "Anatoly Sorokin"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
  html_document: default
params:
  format: !r if(opts_knit$get("rmarkdown.pandoc.to") == 'html') c('screen', 'print')
    else 'print'
  version: !r if(nchar(Sys.which("git"))) system("git describe --long --dirty --abbrev=10  --tags  --always",
    intern=TRUE) else date()
header-includes:
- \usepackage[T2A]{fontenc}
- \usepackage[utf8]{inputenc}
- \usepackage[english,russian]{babel}
- \usepackage{grffile}
- \usepackage{rotating}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage{lscape}
---
```{r loadPackages, include=FALSE, cache=FALSE}
## load additional packages in this chunk
library(pander)
library(knitr)
#library('Matrix')
library(ggplot2)
library(data.table)
#library(plyr)
library(xtable)
#library(xcms)
#library("FactoMineR")
#library(cluster)
#library(dendextend)
#library(factoextra)
#library(corrplot)
library(ncdf4)
#library("PerformanceAnalytics")
#library("pvclust")
#library("sda")
library(RColorBrewer)
library(MALDIquant)
library(MALDIquantForeign)
library(DBI)
library(MonetDBLite)
ticThreshold<-0.01
absTicThreshold<-1000
```

```{r setup, include=FALSE, cache=FALSE}
## This chunk should contain global configuration commands.
## Use this to set knitr options and related things. Everything
## in this chunk will be included in an appendix to document the
## configuration used.
#output <- opts_knit$get("rmarkdown.pandoc.to")
opts_knit$set(stop_on_error = 2L)

## By default R code is only included in HTML versions of the report
## (where it can be collapsed). You can generate a PDF version
## using rmarkdown::pdf_document to get a copy for print. Extensive
## chunks of R code may or may not be desired in /hat setting. If you
## want them simply change the following arguments to `echo = TRUE`.
## In either case the default can be overwritten for individual chunks.
#opts_chunk$set(echo = output=="html")
#opts_chunk$set(warning = output=="html")
#opts_chunk$set(message = output=="html")

## Cache options
opts_chunk$set(cache=FALSE)

## Figure options
## Set default figure format
#options(reportmd.figure.format=params$format)

## Set 'hide.fig.code' to FALSE to include code chunks that
## produce Figures in the output. Note that this affects all chunks
## that provide a figure caption.
opts_chunk$set(hold=TRUE, hide.fig.code=FALSE)

## Set up default plotting options for different formats.
## These can be overwritten for individual chunks
#interactiveFig()
#screenFig()
#printFig()

## Pander options
panderOptions("digits", 3)
panderOptions("table.split.table", 160)
#panderOptions("table.style", "grid")

## Configure Figure and Table lables
#options(figcap.prefix = "Figure", figcap.sep = ":", figcap.prefix.highlight = "**")
#options(tabcap.prefix = "Table", tabcap.sep = ":", tabcap.prefix.highlight = "**")

## Install required knitr hooks
#installHooks()
```

```{r functions, include=FALSE}
## Custom functions used in the analysis should go into this chunk.
## They will be listed in their own section of the appendix.

##==================== Functions ====================##
panderDict<-function(d){
  w<-dim(d)[2]
  pander(d, justify = c('right', rep('left', w-1)))
}
panderCnt<-function(d){
  w<-dim(d)[2]
  inCol<-sapply(d,is.numeric)
  j<-rep('left',w)
  j[inCol]<-'right'
  pander(d, justify = j)
}
##===================== Queries =====================##
diagnosisQ<-paste('select diagnosis,diagnosis.name as diagname,',
'       count(distinct tissue.patientid) cntpat,',
'       count(distinct s.id) cntsamp, count(distinct p.id) cntspec ',
'    from tissue join diagnosis on tissue.diagnosis=diagnosis.id ',
'                left join smpl s on s.tumorid=tissue.id left ',
'                join spectrum p on p.sampletumorid=tissue.id ',
'    group by diagnosis,diagname ',
'    order by cntspec desc;')

```
dtPath = '/Volumes/AS_WD_HFS/Scalpel/DBData/'
cdf.file<-"/Volumes/AS_WD_HFS/Scalpel/BD_cdf/0_00_1178-15_FT100k.cdf"
devID<-1 #Device
solID<-6 #Solvent
isID<-1 # ionsource
resID<-1 #ResolutionID
smplID<-1 #SampleID
stID<-1 #SampleTumorID
stpID<-1 #SampleTumorPatientID
nMode<-1 #Negative mode
rangeID<-1 #MZrange
specID<-'name of the spec' # 
cdf.fname
```

```{r}
dbname<-'msinvent'
usr<-'msinvent'
pwd<-'msinvent'
host<-'192.168.5.133'
```

# Read data
Before running the code a number of variables should be setted for appropriate data loading:
 
 3. the name of the database *dbname*
 4. user/password for teh database: *usr* and *pwd*
 


```{r check.values}
if(!(exists('dbname')&
     exists('host')&
     exists('usr')&
     exists('pwd'))){
  stop('not all obligatory parameters are provided\n')
}
```

# Connect to the database

```{r db.connect}
conn <- dbConnect(MonetDBLite::MonetDB.R(),
dbname = dbname,host=host,
user=usr,password=pwd)
```

# Dictionaries
```{r load.dictionaries,cache=FALSE}
devices<-dbReadTable(conn,'device')
solvents<-dbReadTable(conn,'solvent')
ionSources<-dbReadTable(conn,'ionsource')
resolutions<-dbReadTable(conn,'resolution')
modes<-dbReadTable(conn,'mode')
ranges<-dbReadTable(conn,'mzrange')
```

## Devices
```{r devices.tbl}
panderDict(devices)
```


## Solvents
```{r solvents.tbl}
panderDict(solvents)
```

## Ion Sources
```{r ionSources.tbl}
panderDict(ionSources)
```

## resolutions
```{r resolutions.tbl}
panderDict(resolutions)
```


## Modes
```{r modes.tbl}
panderDict(modes)
```


## ranges
```{r ranges.tbl}
panderDict(ranges)
```

# Basic statistics
```{r diag, cache=FALSE}
dCnt<-dbGetQuery(conn,diagnosisQ)
panderCnt(dCnt)
```


# Appendix {.tabset}
## Functions
```{r functions, eval=FALSE, include=TRUE}
```

## Setup R
```{r setup, eval=FALSE}
```

## Versions
### Document version
```{r docVersion, echo=FALSE, results='asis', cache=FALSE}
cat(params$version)
```

### Session Info
```{r sessionInfo, echo=FALSE, results='asis', class='text', warning=FALSE}
pander(devtools::session_info())
```

