---
title: "scalpelDB report"
author: "Anatoly Sorokin"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
  html_document: default
params:
  format: !r if(opts_knit$get("rmarkdown.pandoc.to") == 'html') c('screen', 'print')
    else 'print'
  version: !r if(nchar(Sys.which("git"))) system("git describe --long --dirty --abbrev=10  --tags  --always",
    intern=TRUE) else date()
header-includes:
- \usepackage[T2A]{fontenc}
- \usepackage[utf8]{inputenc}
- \usepackage[english,russian]{babel}
- \usepackage{grffile}
- \usepackage{rotating}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage{lscape}
---
```{r loadPackages, include=FALSE, cache=FALSE}
## load additional packages in this chunk
library(pander)
library(knitr)
#library('Matrix')
library(ggplot2)
library(data.table)
#library(plyr)
library(xtable)
#library(xcms)
#library("FactoMineR")
#library(cluster)
#library(dendextend)
#library(factoextra)
#library(corrplot)
library(ncdf4)
#library("PerformanceAnalytics")
#library("pvclust")
#library("sda")
library(RColorBrewer)
library(MALDIquant)
library(MALDIquantForeign)
library(DBI)
library(MonetDBLite)
ticThreshold<-0.01
absTicThreshold<-1000
```

```{r setup, include=FALSE, cache=FALSE}
## This chunk should contain global configuration commands.
## Use this to set knitr options and related things. Everything
## in this chunk will be included in an appendix to document the
## configuration used.
#output <- opts_knit$get("rmarkdown.pandoc.to")
opts_knit$set(stop_on_error = 2L)

## By default R code is only included in HTML versions of the report
## (where it can be collapsed). You can generate a PDF version
## using rmarkdown::pdf_document to get a copy for print. Extensive
## chunks of R code may or may not be desired in /hat setting. If you
## want them simply change the following arguments to `echo = TRUE`.
## In either case the default can be overwritten for individual chunks.
#opts_chunk$set(echo = output=="html")
#opts_chunk$set(warning = output=="html")
#opts_chunk$set(message = output=="html")

## Cache options
opts_chunk$set(cache=FALSE)

## Figure options
## Set default figure format
#options(reportmd.figure.format=params$format)

## Set 'hide.fig.code' to FALSE to include code chunks that
## produce Figures in the output. Note that this affects all chunks
## that provide a figure caption.
opts_chunk$set(hold=TRUE, hide.fig.code=FALSE)

## Set up default plotting options for different formats.
## These can be overwritten for individual chunks
#interactiveFig()
#screenFig()
#printFig()

## Pander options
panderOptions("digits", 3)
panderOptions("table.split.table", 160)
#panderOptions("table.style", "grid")

## Configure Figure and Table lables
#options(figcap.prefix = "Figure", figcap.sep = ":", figcap.prefix.highlight = "**")
#options(tabcap.prefix = "Table", tabcap.sep = ":", tabcap.prefix.highlight = "**")

## Install required knitr hooks
#installHooks()
```

```{r functions, include=FALSE}
## Custom functions used in the analysis should go into this chunk.
## They will be listed in their own section of the appendix.

##==================== Functions ====================##
panderDict<-function(d){
  w<-dim(d)[2]
  pander(d, justify = c('right', rep('left', w-1)))
}
panderCnt<-function(d){
  w<-dim(d)[2]
  inCol<-sapply(d,is.numeric)
  j<-rep('left',w)
  j[inCol]<-'right'
  pander(d, justify = j)
}
plotPie<-function(x,label,main='',th=1){
  pr<-100*x/sum(x)
  idx<-which(pr>=th)
  xx<-x[idx]
  lx<-label[idx]
  ord<-order(xx,decreasing = TRUE)
  xx<-xx[ord]
  lx<-lx[ord]
  xx<-c(xx,sum(x[-idx]))
  lx<-c(lx,'Other')
  graphics::pie(xx,lx,main=main)
}
```

```{r queries, include=FALSE}
##===================== Queries =====================##
diagnosisQ<-paste('select diagnosis,diagnosis.name as diagname,',
'       count(distinct tissue.patientid) cntpat,',
'       count(distinct s.id) cntsamp, count(distinct p.id) cntspec ',
'    from tissue join diagnosis on tissue.diagnosis=diagnosis.id ',
'                left join smpl s on s.tumorid=tissue.id left ',
'                join spectrum p on p.sampletumorid=tissue.id ',
'    group by diagnosis,diagname ',
'    order by cntspec desc;')
expTypeQ<-paste('select  exptype,e.name as expname',
'      ,count(distinct tissue.patientid) cntpat',
'      ,count(distinct s.id) cntsamp ',
'      ,count(distinct p.id) cntspec ',
'   from tissue left join smpl s on',
'      s.tumorid=tissue.id left join spectrum p on',
'      p.sampletumorid=tissue.id join exptype e on',
'      p.exptype=e.id',
'   group by exptype,expname order by cntspec desc')
ionSourceQ<-paste('select  ionsource,e.name as name',
'      ,count(distinct tissue.patientid) cntpat',
'      ,count(distinct s.id) cntsamp ',
'      ,count(distinct p.id) cntspec ',
'   from tissue left join smpl s on',
'      s.tumorid=tissue.id left join spectrum p on',
'      p.sampletumorid=tissue.id join ionsource e on',
'      p.ionsource=e.id',
'   group by ionsource,name order by cntspec desc')
resQ<-paste('select  resolutionid,e.name as name',
'      ,count(distinct tissue.patientid) cntpat',
'      ,count(distinct s.id) cntsamp ',
'      ,count(distinct p.id) cntspec ',
'   from tissue left join smpl s on',
'      s.tumorid=tissue.id left join spectrum p on',
'      p.sampletumorid=tissue.id join resolution e on',
'      p.resolutionid=e.id',
'   group by resolutionid,name order by cntspec desc')
specTotQ<-paste('select s.id,sampletumorid,sampletumorpatientid,sampleid,',
'diagnosis.name as diagname,r.name as res,i.name as ionsource, ',
'm.name as mode, e.name as exptype',
'from spectrum s join tissue on sampletumorid=tissue.id ',
'join diagnosis on tissue.diagnosis=diagnosis.id',
'join ionsource i on s.ionsource=i.id ',
'join resolution r on r.id=resolutionid ',
'join mode m on m.id=s.mode ',
'join exptype e on e.id=s.exptype')

emptyPeaksQ0<-paste('select s.id,filename,',
                    'count(distinct c.id) scn,',
                    'count(distinct p.id) pnt ',
                    'from spectrum s left join scan c on s.id=c.spectrumid ',
                    'left join peak p on p.scan=c.id ',
                    'group by s.id,filename',
                    'having count(distinct p.id)=0',
                    'order by s.id asc;')
emptyPeaksQ<-paste('select s.id,filename, ',
                   'count(distinct c.id) scn  ',
                   'from spectrum s join scan c ',
                   'on s.id=c.spectrumid ',
                   'where c.id in ',
                   '(select id as scan from scan ',
                   'except select scan from peak) ',
                   'group by s.id,filename ',
                   'order by filename')
emptyScansQ<-paste('select s.id,filename,count(distinct c.id) scans',
                   'from spectrum s left join scan c on s.id=c.spectrumid ',
                   'group by s.id,filename having count(distinct c.id)=0;')
########### NULL-IN queries #############
ni.diag<-'select id,label,grade,dt,histdiag from tissue where diagnosis=1'
ni.mzrange<-'select id,mzrange,dt,filename  from spectrum where mzrange is null'
ni.mode<-'select id,mode,dt,filename  from spectrum where mode is null'
ni.exptype<-'select id,exptype,dt,filename  from spectrum where exptype is null'
```

```{r echo=FALSE, include=FALSE}
dbname<-'msinvent'
usr<-'msinvent'
pwd<-'msinvent'
host<-'192.168.5.133'
```

# Read data
Before running the code a number of variables should be setted for appropriate data loading:
 
 3. the name of the database *dbname*
 4. user/password for teh database: *usr* and *pwd*
 


```{r check.values}
if(!(exists('dbname')&
     exists('host')&
     exists('usr')&
     exists('pwd'))){
  stop('not all obligatory parameters are provided\n')
}
```

# Connect to the database

```{r db.connect}
conn <- dbConnect(MonetDBLite::MonetDB.R(),
dbname = dbname,host=host,
user=usr,password=pwd,timeout=2400)
```

# Dictionaries
```{r load.dictionaries,cache=FALSE}
devices<-dbReadTable(conn,'device')
solvents<-dbReadTable(conn,'solvent')
ionSources<-dbReadTable(conn,'ionsource')
resolutions<-dbReadTable(conn,'resolution')
modes<-dbReadTable(conn,'mode')
ranges<-dbReadTable(conn,'mzrange')
spectrum<-dbReadTable(conn,'spectrum')
```

## Devices
```{r devices.tbl}
panderDict(devices)
```


## Solvents
```{r solvents.tbl}
panderDict(solvents)
```

## Ion Sources
```{r ionSources.tbl}
panderDict(ionSources)
```

## resolutions
```{r resolutions.tbl}
panderDict(resolutions)
```


## Modes
```{r modes.tbl}
panderDict(modes)
```


## ranges
```{r ranges.tbl}
panderDict(ranges)
```

# Basic statistics
## Counts
```{r diag, cache=FALSE}
dCnt<-dbGetQuery(conn,diagnosisQ)
cntpat=sum(dCnt$cntpat)
cntsamp=sum(dCnt$cntsamp)
cntspec=sum(dCnt$cntspec)
dCnt<-rbind(dCnt,
            data.frame(diagnosis=NA,
                       diagname='Total',
                       cntpat=sum(dCnt$cntpat),
                       cntsamp=sum(dCnt$cntsamp),
                       cntspec=sum(dCnt$cntspec)))
panderCnt(dCnt)
```

## Percent
```{r diag.perc}
dPerc<-dCnt
dPerc$cntpat<-100*dCnt$cntpat/cntpat
dPerc$cntsamp<-100*dCnt$cntsamp/cntsamp
dPerc$cntspec<-100*dCnt$cntspec/cntspec
panderCnt(dPerc)
```


## Diagnosis over Patients
```{r diag.cntpat.pie,fig.width=11,fig.height=11}
plotPie(dCnt$cntpat,dCnt$diagname,main='Patients')
```

## Diagnosis over Samples
```{r diag.cntsmpl.pie,fig.width=11,fig.height=11}
plotPie(dCnt$cntsamp,dCnt$diagname,main='Samples')
```

## Diagnosis over Spectra
```{r diag.cntspec.pie,fig.width=11,fig.height=11}
plotPie(dCnt$cntspec,dCnt$diagname,main='Spectra')
```



```{r exT, cache=FALSE}
etCnt<-dbGetQuery(conn,expTypeQ)
panderCnt(etCnt)
```

```{r is, cache=FALSE}
isCnt<-dbGetQuery(conn,ionSourceQ)
panderCnt(isCnt)
```

```{r res, cache=FALSE}
resCnt<-dbGetQuery(conn,resQ)
panderCnt(resCnt)
```


```{r specT, cache=FALSE}
spec<-dbGetQuery(conn,specTotQ)
qplot(diagname,data = spec,facets = .~res)+coord_flip()
qplot(diagname,data = spec,facets = .~ionsource)+coord_flip()
qplot(diagname,data = spec,facets = .~exptype)+coord_flip()
qplot(diagname,data = spec,facets = .~mode)+coord_flip()
qplot(diagname,data = spec,facets = res~mode)+coord_flip()
```

## Pie charts
### LTQ
```{r spect.ltq.pie,fig.height=11,fig.width=11}
x<-table(subset(spec,res=='LTQ',select = 'diagname'));plotPie(x,names(x),main='LTQ')
x<-table(subset(spec,res=='LTQ'&mode=='negative',select = 'diagname'));plotPie(x,names(x),main='Negative LTQ')
x<-table(subset(spec,res=='LTQ'&mode=='positive',select = 'diagname'));plotPie(x,names(x),main='Positive LTQ')
x<-table(subset(spec,res=='LTQ'&exptype=='fresh',select = 'diagname'));plotPie(x,names(x),main='Fresh LTQ')
x<-table(subset(spec,res=='LTQ'&exptype=='frozen',select = 'diagname'));plotPie(x,names(x),main='Frozen LTQ')
```

### FT
```{r spect.ft.pie,fig.height=11,fig.width=11}
x<-table(subset(spec,res=='FT',select = 'diagname'));plotPie(x,names(x),main='FT')
x<-table(subset(spec,res=='FT'&mode=='negative',select = 'diagname'));plotPie(x,names(x),main='Negative FT')
x<-table(subset(spec,res=='FT'&mode=='positive',select = 'diagname'));plotPie(x,names(x),main='Positive FT')
```

### FT


```{r spec.pie,fig.height=11,fig.width=11}
orig<-par(mfrow = c(2,2))
x<-table(subset(spec,res=='FT'&mode=='negative',select = 'diagname'));plotPie(x,names(x),main='Negative FT',th=2)
x<-table(subset(spec,res=='FT'&mode=='positive',select = 'diagname'));plotPie(x,names(x),main='Positive FT',th=2)
x<-table(subset(spec,res=='LTQ'&mode=='negative',select = 'diagname'));plotPie(x,names(x),main='Negative LTQ',th=2)
x<-table(subset(spec,res=='LTQ'&mode=='positive',select = 'diagname'));plotPie(x,names(x),main='Positive LTQ',th=2)
par(orig)
```


# Possible errors and data inconsistencies

## Empty spectra
```{r empty.spectra}
resNI<-dbGetQuery(conn,emptyScansQ)
panderCnt(resNI)
```

## Empty scans
```{r empty.scans}
resNI<-dbGetQuery(conn,emptyPeaksQ)
resNI$fn<-sub('_[0-9]+$','',resNI$filename)
panderCnt(as.data.table(resNI)[,.(N=length(id),cnt=length(unique(id)),scn=sum(scn)),by=.(fn)])
panderCnt(resNI)
```

## Missing data

### Null in Diagnosis
```{r ni.diag}
resNI<-dbGetQuery(conn,ni.diag)
panderCnt(resNI)
```

### Null in MZrange
```{r ni.mzrange}
resNI<-dbGetQuery(conn,ni.mzrange)
panderCnt(resNI)
```

### Null in Mode
```{r ni.mode}
resNI<-dbGetQuery(conn,ni.mode)
panderCnt(resNI)
```

### Null in Type Experiment
```{r ni.expt}
resNI<-dbGetQuery(conn,ni.exptype)
panderCnt(resNI)
```

# Appendix {.tabset}
## Functions
```{r functions, eval=FALSE, include=TRUE}
```
```{r queries, eval=FALSE, include=TRUE}
```

## Setup R
```{r setup, eval=FALSE}
```

## Versions
### Document version
```{r docVersion, echo=FALSE, results='asis', cache=FALSE}
cat(params$version)
```

### Session Info
```{r sessionInfo, echo=FALSE, results='asis', class='text', warning=FALSE}
pander(devtools::session_info())
```

